A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-08 revisionNotel2_responses.tex
rebuttal for reviewer #3 (round 1 2)

This bioinformatics paper is providing targets and hints for the in vitro and in vivo validation.
We open invitation of research community by strongly support their rationale for looking into these HNSCC candidates.
%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
%the rest of the analysis seems fine, but 
%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
We also aim to promote a reproducible research\cite{Preeyanon2014} with this workflow which will apply on their in-house HNSCC database to find more useful biomarkers. % or even other cancer types
why reproducibility?

Once those candidates are identified as the target, the compound screening could help to discover a potential drug for HNSCC therapy.
%https://www.mdpi.com/journal/cancers/instructions

@@

%usually, only one round of major revisions is allowed. Authors will be asked to resubmit the revised paper within a suitable time frame, and the revised version will be returned to the reviewer for further comments.

>>>>

% 其實文章真正的目標是  bioinformatics workflow，而不是 discovered biomarkers itself (see TCGA marker paper\cite{Lawrence2015a})
Moreover, this bioinformatics paper is providing targets and supporting community's rationale for looking into these HNSCC candidates by in vitro and in vivo validation. %Collectively, these findings provide new insights into HNSCC and suggest that shared and unique alterations might be leveraged to accelerate progress in prevention and therapy across tumour types\cite{Lawrence2015a}.
%We open invitation for research community by potential support their rationale for looking into these HNSCC candidates.
%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
%the rest of the analysis seems fine, but 
%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
We aim to promote a reproducible bioinformatics\cite{Preeyanon2014}\cite{Kulkarni2018} workflow allowing successful repetition and extension of analyses based on TCGA or their in-house HNSCC dataset. % to find more useful biomarkers. % or even other cancer types
% to allow successful repetition and extension of analyses based on original data
A good practice of research reproducibility is necessary in order to allow %previously developed methodology to be effectively applied on new data, or to allow 
reuse of code and results for new projects. %In other words, good habits of reproducibility
It may actually turn out to be a time-saver in the longer run.
When a result can be reproduced by multiple scientists, it will also validate our original results and readiness to progress to the next phase of research. 
%why reproducibility?
%Reproducible Bioinformatics Project provides a general schema and an infrastructure to distribute robust and reproducible workflows. Thus, it guarantees to final users the ability to repeat consistently any analysis independently by the used UNIX-like architecture.
%Utility of this model would facilitate development of more individualized therapy for HNSCC patients and improve prognosis.

Once those candidates are identified by Alex's laboratory (or community) as the targets, the compound screening could facilitate development of more individualized therapy for HNSCC patients and improve prognosis. %help to discover a potential drug for HNSCC therapy.
%https://www.mdpi.com/journal/cancers/instructions

@@

%usually, only one round of major revisions is allowed. Authors will be asked to resubmit the revised paper within a suitable time frame, and the revised version will be returned to the reviewer for further comments.
\pagebreak
